THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-09-06 DishReflectometry/Paper1_v3.tex
renamed the paper to avoid marging conflict

Since first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{2015ApJ...801..138P}, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{Bowman_et_al2010},
BIGHORNS; ~\citealt{XXX},
SARAS; ~\citep{Patra_et_al2015} ,
SCIHI; ~\citep{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spectrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
The redshifted 21 cm spatial power spectrum is defined as
\begin{equation}
  P(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
\label{eq:delay-power-spectrum}
\end{equation}
where
\begin{equation}
  k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
  k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
\end{equation}
The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
$f_{21}$:rest frame frequency of the 21~cm radiation.\\
$f$: observation frequency.\\
$z$: cosmological redshift corresponding to the frequency of observation.\\
 $\Delta B$: bandwidth centered at the observation frequency.\\
 $k_\textrm{B}$: Boltzmann constant.\\
 $D\equiv D(z)$ comoving distance along the line of sight\\
 $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
$E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
\indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

@@

An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission. While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq:Sigma} could be measured using the return loss measurement technique with a vector network analyzer (VNA). \\
\section{\textbf{Reflectometry measurements}}

@@

\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{The HERA feed consists of a pair of crossed-dipoles ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}

Return loss measurements are similar to auto correlation measurement from a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.

The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{meas_sim_RL_feed} and figure \ref{meas_sim_RL_HERA}.
\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_mag.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the feed as simulated and measured. While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements. The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input. }   
\label{meas_sim_RL_feed}
\end{figure}

\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_mag.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured. In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band. }   
\label{meas_sim_RL_HERA}
\end{figure}

\section{Results}
\begin{figure}       
\centering
\includegraphics[width=\linewidth]{plots/H_dish_feed.png}
\caption{Delay spectrum of the HERA element (green) the HERA feed (blue) estimated by taking the Fourier transform of the measured return loss of power at the feed output. The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure. After correcting the measurements from the transmission mode to reception mode by equation \ref{eq:power_ratio} the delay spectrum in the receiving mode is estimated (red). }
\label{fig:delay_spectrum}
\end{figure}

Figure \ref{meas_sim_RL_HERA} shows the return loss measured between $100$ to
$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. This measurement is first correc ted to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}. The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}. Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artefacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

@@

\subsection{\textbf{Antenna beam pattern and feed return loss}}
The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum. However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant. During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.  Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{meas_sim_RL_feed}. This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.

\subsection{\textbf{Dish reflections}}
Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish. Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays. The estimated delay spectrum of the instrument is collectively contributed by all the reflections. We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{meas_sim_RL_feed}. Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish. 
 Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays. Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue. At lower delays, the reflections are dominated by the feed structure. Therefore, the delay spectrum in both the cases follow each other. Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$ around which these two delay spectrum starts to deviate. At delays $\> 50nS$ the dish reflections starts to dominate over the reflections from the feed structure and the two delay spectrum deviates from each other.

\subsection{\textbf{Measurement bandwidth and window function}}
Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements. Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function. In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays. Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data. Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window. Windowing the data prior to Fourier transform significantly reduces the system response higher delays.  
\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/window_effect.png}
\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
\label{fig:window}
\end{figure}

@@

While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatched impedance between the feed and the 50 Ohm transmission line. In the delay domain, this appears at the zero delay bin. This response is identical whether or not the feed is suspended on the dish. We can, therefore, quantify this response by measuring the feed return loss while the feed is kept on the ground facing the sky. This results in a feed return loss including the surrounding cage structure but excluding the dish response. While a fraction, $\Gamma_{f}$, of the power is reflected off the feed, $1+\Gamma_{f}$ gets transmitted. In the receiving mode, upon initial incidence, $\Gamma_{f}$ of the voltage is reflected back into free space while $1+\Gamma_{f}$ enters the feed, and, in the delay domain, this appears at the zero delay bin. Using the return loss measurement of the feed $(\Gamma_{f})$ and the return loss measurement, $s_{11}$, of the dish, the feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component, and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. 
%
%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output. The HERA feed design is driven by the PAPER element with an improved response at all delays. The feed, when suspended on the dish, results in a more complex return loss, and the corresponding delay response is shown in the figure.} %Delay units are incorrect!!!! Should be ns not GHz!!!!
\label{fig:delay_spectrum}
\end{figure}

@@

21cm power spectrum measurements are limited by challenges posed by the low frequency radio foreground that is order of magnitude brighter than the expected power spectrum amplitude. While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need for increased sensitivity called for increased collecting area per PAPER element. This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element. Additional limitations on PAPER and its contemporaries are imposed by the spectral structure of the system response. Sky signal is frequency modulated by the system bandpass response. In delay spectrum technique of 21cm power spectrum estimation, sky signal is convolved with the system response in the delay domain. In this process of convolution, the frequency dependent system response with rapid frequency variation results in spreading of the smooth spectrum foreground of the sky signal to the delays in which EoR power spectrum is to be estimated. This essentially limits the capacity of any experiment to probe the smaller spatial scales of fluctuations. \\
	In a related series of papers, the spatial scales of fluctuation $(k_||)$ HERA element delay response has been studied via electromagnetic simulation (deBoer et al 2016) as well as via time domain simulation (Ewall-wice et al 2016). Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows the measurement presented this paper in comparison with the simulations. Simulations and measurements are in good agreement with each other upto around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure. Since the simulated return loss shows a better match of the antenna to the 50 Ohm transmission line. At zero delay , in case of simulation, almost $100\%$ of the sky signal is received whereas in case of measurements, this match is found to be less than $5~dB$ resulting in partial coupling of the sky signal to the system. Given all the reflections unaltered, if the matching in between the feed and the transmission line is improved by about $10~dB$, which is achievable in reality, the delay spectrum would improve substantially. This is plotted in grey. The work is currently under progress to improve the feed return loss at least by  $10dB$ (Eloy et al 2016 in prep?). Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.\\
Thygarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground model as well as model for EoR power spectrum for various simulated antenna element response. The theoretical limits for the level of signal attenuation required in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values. The requirements for the reduced instrument response at higher delays are more stringent for the detection of lower $k_\parallel$ modes. The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$. \\
\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/meas_forground.png}
\caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
\label{fig:sim_fg}
\end{figure}

>>>>

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{2015ApJ...801..138P}, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{Bowman_et_al2010},
BIGHORNS; ~\citealt{XXX},
SARAS; ~\citep{Patra_et_al2015} ,
SCIHI; ~\citep{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spectrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
The redshifted 21 cm spatial power spectrum is defined as
\begin{equation}
  P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
\label{eq:delay-power-spectrum}
\end{equation}
where
\begin{equation}
  k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
  k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
\end{equation}
The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
$f_{21}$:rest frame frequency of the 21~cm radiation.\\
$f$: observation frequency.\\
$z$: cosmological redshift corresponding to the frequency of observation.\\
 $\Delta B$: bandwidth centered at the observation frequency.\\
 $k_\textrm{B}$: Boltzmann constant.\\
 $D\equiv D(z)$ comoving distance along the line of sight\\
 $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
$E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
\indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

@@

An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission. While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq:Sigma} could be measured using the return loss measurement technique with a vector network analyzer (VNA). \\

\section{\textbf{Reflectometry measurements}}

@@

\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{The HERA feed consists of a pair of crossed-dipoles over 1.72 mt diameter backplane made of wire mesh. The backplane is surrounded by 0.36 m wide wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}

\section{Results}
Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.

The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{RL_mag_feed} and figure \ref{RL_mag_dish}. The measurements deviates from the simulated performance in one major aspect. While the return loss of the simulated structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies. While the simulated response shows very wide resonant peaks, as expected from these dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance. This feature somewhat dominates the fall off rate in the delay response of the system bandpass. The delay response of the feed alone is shown in figure \ref{ds_feed_on_dish_trans} along with the delay response of a HERA element in transmission mode. In the following sections, we compute the response of the HERA element in the receiving mode. 
\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/RL_mag_feed.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the feed as simulated and measured. While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements. The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input. }   
\label{RL_mag_feed}
\end{figure}

\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/RL_mag_dish.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured. In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band. }   
\label{RL_mag_dish}
\end{figure}

\begin{figure}       
\centering
\includegraphics[width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/ds_feed_on_dish_trans_recp.png}
\caption{Delay spectrum of the HERA feed (brown) estimated by taking the Fourier transform of the measured return loss of power at the feed output. The feed, when suspended on the dish results in a more complex return loss as shown in figure \ref{RL_mag_dish} and corresponding delay response is shown here in black. This figure shows the delay spectrum of the instrument in the as estimated from direct measurements of the return loss i.e, in the transmission mode of the antenna. }
\label{ds_feed_on_dish_trans}
\end{figure}

Figure \ref{RL_mag_dish} shows the measured return loss when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. The measured return loss is much more complex than what is found from the simulation. The delay spectrum in the transmission mode is shown in \ref{ds_feed_on_dish_trans}. To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}. The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}. Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artfacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

@@

%\subsection{\textbf{Antenna beam pattern and feed return loss}}
%The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum. However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant. 
During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.  Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 4:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{RL_feed_mag}. This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.

\subsection{\textbf{Dish reflections}}
Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish. Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays. The estimated delay spectrum of the instrument is collectively contributed by all the reflections. Delay spectrum estimated from the return loss measurement of the feed alone,  provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish. 
From figure \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by the feed structure. Therefore, the delay spectrum in both the cases follow each other. Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$ around which these two delay spectrum starts to deviate. At delays $\> 50nS$ the dish reflections starts to dominate over the reflections from the feed structure and the two delay spectrum deviates from each other.

\subsection{\textbf{Measurement bandwidth and window function}}
Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements. Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function. In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays. Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data. Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window. Windowing the data prior to Fourier transform significantly reduces the system response higher delays.  
\begin{figure}
\centering
\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
\label{fig:window}
\end{figure}

@@

%While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatched impedance between the feed and the 50 Ohm transmission line. In the delay domain, this appears at the zero delay bin. This response is identical whether or not the feed is suspended on the dish. We can, therefore, quantify this response by measuring the feed return loss while the feed is kept on the ground facing the sky. This results in a feed return loss including the surrounding cage structure but excluding the dish response. While a fraction, $\Gamma_{f}$, of the power is reflected off the feed, $1+\Gamma_{f}$ gets transmitted. In the receiving mode, upon initial incidence, $\Gamma_{f}$ of the voltage is reflected back into free space while $1+\Gamma_{f}$ enters the feed, and, in the delay domain, this appears at the zero delay bin. Using the return loss measurement of the feed $(\Gamma_{f})$ and the return loss measurement, $s_{11}$, of the dish, the feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component, and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. 
%
%
%\begin{figure}[ht]
%\centering
%\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
%\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output. The HERA feed design is driven by the PAPER element with an improved response at all delays. The feed, when suspended on the dish, results in a more complex return loss, and the corresponding delay response is shown in the figure.} %Delay units are incorrect!!!! Should be ns not GHz!!!!
%\label{fig:delay_spectrum}
%\end{figure}

@@

21cm power spectrum measurements are limited by challenges posed by the low frequency radio foreground that is order of magnitude brighter than the expected power spectrum amplitude. While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need for increased sensitivity called for increased collecting area per PAPER element. This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element. Additional limitations on PAPER and its contemporaries are imposed by the spectral structure of the system response. Sky signal is frequency modulated by the system bandpass response. In delay spectrum technique of 21cm power spectrum estimation, sky signal is convolved with the system response in the delay domain. In this process of convolution, the frequency dependent system response with rapid frequency variation results in spreading of the smooth spectrum foreground of the sky signal to the delays in which EoR power spectrum is to be estimated. This essentially limits the capacity of any experiment to probe the smaller spatial scales of fluctuations. \\
	In a related series of papers, the spatial scales of fluctuation $(k_||)$ HERA element delay response has been studied via electromagnetic simulation (deBoer et al 2016) as well as via time domain simulation (Ewall-wice et al 2016). Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows the measurement presented this paper in comparison with the simulations. Simulations and measurements are in good agreement with each other upto around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure. Since the simulated return loss shows a better match of the antenna to the 50 Ohm transmission line. At zero delay , in case of simulation, almost $100\%$ of the sky signal is received whereas in case of measurements, this match is found to be less than $5~dB$ resulting in partial coupling of the sky signal to the system. Given all the reflections unaltered, if the matching in between the feed and the transmission line is improved by about $10~dB$, which is achievable in reality, the delay spectrum would improve substantially. This is plotted in grey. The work is currently under progress to improve the feed return loss at least by  $10dB$ (Eloy et al 2016 in prep?). Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.\\
Thyagarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground model as well as model for EoR power spectrum for various simulated antenna element response. The sensitivity is quantified as a ratio of EoR signal power to the foreground power at various $\bold k_{\parallel}$ mode i.e at various delays. The theoretical limits for the level of foreground attenuation required relative to the EoR signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values.  The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$ over a bandwidth of $10~MHz$. This simulation shows the effect of chromatic antenna response and how that contaminates the delay modes beyond the horizon limit. Thus, this establishes a very stringent limits of required foreground attenuation relative to EoR signal which demands almost an ideal system performance. \\
%As shown in section (), multiple reflection in the antenna system generates multiple copies of the sky signal and thus results in additional foreground contaminations in the delay modes where EOR power spectrum is measurable in case of no reflections. Reflectometry measurements shows the relative strength with which the multiple copies of the signal shows up at various delays.
